---
title: "Homework - features and elements of multiple regression"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

<hr>

# MVP

1. Load the `diamonds.csv` data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant [Kaggle page](https://www.kaggle.com/shivam2503/diamonds/)

```{r}
library(tidyverse)
library(GGally)
diamonds <- read_csv("data/diamonds.csv")
```


<br>

2. We expect the `carat` of the diamonds to be strong correlated with the physical dimensions `x`, `y` and `z`. Use `ggpairs()` to investigate correlations between these four variables.

```{r}
ggpairs(diamonds)
```


<br>

3. So, we do find significant correlations. Let's drop columns `x`, `y` and `z` from the dataset, in preparation to use only `carat` going forward.

```{r}
diamonds <- diamonds %>% 
  select(-c("x", "y", "z"))
```


<br>

4. We are interested in developing a regression model for the `price` of a diamond in terms of the possible predictor variables in the dataset. 

  i. Use `ggpairs()` to investigate correlations between `price` and the predictors (this may take a while to run, don't worry, make coffee or something).
  
```{r}
ggpairs(diamonds)
```
  

  ii. Perform further `ggplot` visualisations of any significant correlations you find.
  
```{r}
diamonds %>% 
  ggplot(aes(x = price, y = carat)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE)

diamonds %>% 
  ggplot(aes(x = price, y = color)) +
  geom_boxplot()
```


  
<br>

5. Shortly we may try a regression fit using one or more of the categorical predictors `cut`, `clarity` and `color`, so let's investigate these predictors: 

  i. Investigate the factor levels of these predictors. How many dummy variables do you expect for each of them?
  
```{r}
# 5
diamonds %>% 
  distinct(cut)
```
  
```{r}
# 8
diamonds %>% 
  distinct(clarity)
```

```{r}
# 7 
diamonds %>% 
  distinct(color)
```


  ii. Use the `dummy_cols()` function in the `fastDummies` package to generate dummies for these predictors and check the number of dummies in each case.

```{r}
library(fastDummies)

diamonds %>%  
  dummy_cols(select_columns = "cut",
             remove_selected_columns = TRUE)

diamonds %>%  
  dummy_cols(select_columns = "clarity",
             remove_selected_columns = TRUE)

diamonds %>%  
  dummy_cols(select_columns = "color",
             remove_selected_columns = TRUE)
```

    
6. Start with simple linear regression. Regress `price` on `carat` and check the regression diagnostics.

```{r}
library(ggfortify)

model <- lm(price ~ carat, data = diamonds)

autoplot(model)

summary(model)
```


<br>


7. Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.

```{r}
# Carat and Color are both 3 * P Values so significant. 86% R-Squared value so high.
model2 <- lm(price ~ carat + color, data = diamonds)

autoplot(model2)

summary(model2)
```

    
<hr>


# Extension
    
8. Try adding an interaction between `log(carat)` and your chosen categorical predictor. Do you think this interaction term is statistically justified?

<br>

9. Find and plot an appropriate visualisation to show the effect of this interaction
    