---
title: "Weekend Homework - Model Building"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

# MVP

We've looked at a few different ways in which we can build models this week, including how to prepare them properly. This weekend we'll build a multiple linear regression model on a dataset which will need some preparation. The data can be found in the data folder, along with a data dictionary

We want to investigate the avocado_trim dataset, and, in particular, to model the `AveragePrice` of the avocado_trims. Use the tools we've worked with this week in order to prepare your dataset and find appropriate predictors. Once you've built your model use the validation techniques discussed on Wednesday to evaluate it. Feel free to focus either on building an *explanatory* or a *predictive* model, or both if you are feeling energetic!

As part of the MVP we want you not to just run the code but also have a go at **interpreting the results** and write your thinking in comments in your script.

**Hints and tips**

* `region` may lead to many dummy variables. Think carefully about whether to include this variable or not (there is no one 'right' answer to this!)
* Think about whether each variable is *categorical* or *numerical*. If categorical, make sure that the variable is represented as a factor.
* We will not treat this data as a time series, so `Date` will not be needed in your models, but can you extract any useful features out of `Date` before you discard it?
* If you want to build a predictive model, consider using either `leaps` or `glmulti` to help with this.

```{r}
library(tidyverse)
library(lubridate)
library(fastDummies)
library(ggfortify)
library(modelr)
library(leaps)
library(caret)
```

```{r}
# Loading data
avocado <- read.csv("data/avocado.csv") 

#Tidy up
avocado_trim <- avocado %>% 
  mutate(month = month(Date), # Remove month from Date column
         year = as.factor(year), # Set year as a factor
         month = as.factor(month)) %>%  # Set month as a factor
  select(-c("X", "Date")) %>% # Remove unneeded columns
  # Create dummy columns for region and type 
  dummy_cols(select_columns = "region", remove_first_dummy = TRUE, remove_selected_columns = TRUE) %>% 
  dummy_cols(select_columns = "type", remove_first_dummy = TRUE, remove_selected_columns = TRUE) 
  
```

```{r}
# Checked for any variables with relationships. Date and year did. Removed month from Date then removed Date (above)
alias(lm(AveragePrice ~ ., avocado_trim))
```

```{r}
# Created forward model selection
regsubsets_forward <- regsubsets(AveragePrice ~ ., data = avocado_trim, nvmax = 20, method = "forward")
```

```{r}
# Looked at the summary
sum_regsubsets_forward <- summary(regsubsets_forward)
sum_regsubsets_forward
```

```{r}
sum_regsubsets_forward$which
```

```{r}
# Looked at adjusted r 2 to see which variables to include
plot(regsubsets_forward, scale = "adjr2")
```

```{r}
# Looked at bic to see which variables to include
plot(regsubsets_forward, scale = "bic")
```

```{r}
# Plotted to find the 'elbow' to see how many variable to use. Unfortunately isn't a clear one in this data
plot(sum_regsubsets_forward$rsq, type = "b")
```

```{r}
# Plotted to find the 'elbow' to see how many variable to use. Unfortunately isn't a clear one in this data
plot(sum_regsubsets_forward$bic, type = "b")
```

```{r}
# Began building the model using the above insights
model_1 <- lm(AveragePrice ~ type_organic, data = avocado_trim)
summary(model_1)
```

```{r}
# Checking the plots. Looking great here.
autoplot(model_1)
```

```{r}
# Adding another variable
model_2 <- lm(AveragePrice ~ type_organic + year, data = avocado_trim)
summary(model_2)
```

```{r}
# Sitll looking going. Tails coming off in the Normal Q-Q a little. Slight bend in the Scale-Location line. Still looing great. 
autoplot(model_2)
```

```{r}
# Ran an anova to check significance. *** ideal
anova(model_1, model_2)
```

```{r}
# Added another. Adj R Squared isn't increasing that much now. 
model_3 <- lm(AveragePrice ~ type_organic + year + region_HartfordSpringfield, data = avocado_trim)
summary(model_3)
```

```{r}
# The Scale-Location isn't looking great now but still probably ok to use.
autoplot(model_3)
```

```{r}
# Checked significant. Still fine.
anova(model_2, model_3)
```

```{r}
# Added another variable. Small adj r 2 increase.
model_4 <- lm(AveragePrice ~ type_organic + year + region_HartfordSpringfield + region_SanFrancisco, data = avocado_trim)
summary(model_4)
```

```{r}
# Scale-Location not looking great. I'd probably end the model here.
autoplot(model_4)
```

```{r}
# Still significant.
anova(model_3, model_4)
```

With there being no clear 'elbow' in the data on the plots we ran it's hard to know when to clearly stop building on this model and when overfitting happens. I'd say model 3 or 4 are fine but model 2 looked best. 
