---
title: "Introduction to `ggplot2` homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
    pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

# Homework Info

This homework recaps what you learnt in class today. 

You'll be looking at the `backpack` dataset contained within the `CodeClanData` package using tidyverse. You'll need to load the appropriate packages first.In all plots you make, ensure your labels are appropriate 

**You must write down a short summary of what each plot tells you in order to meet MVP.** Being an analyst is not just the ability to write code, you need to be able to interpret the visualisations and translate the relationships found (or not found) into plain language to explain to non-technical decision makers. Getting as much practice of this as you can while on this course is just (if not more!) important than the code!

```{r}
library(tidyverse)
library(CodeClanData)
```



# MVP

<br>

**Question 1.**  

Load in the libraries you need, and look at the `backpack` data. Take note of variable names and dimensions.   

```{r}
backpack <- backpack
```


**Question 2.**

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution. 

```{r}
#This density graph shows that most people have backpacks of around 10kg.

ggplot(backpack) +
  geom_density(aes(backpack_weight)) +
  labs(x = "Backpack Weight",
       y = "Number of Backpacks")
```


**Question 3.**  

Are there differences in backpack weight between sex?   

```{r}
# Broadly similar weight between sex, however males typically carry a slightly heavier backpack

ggplot(backpack) +
  geom_density(aes(backpack_weight, colour = sex)) +
  labs(x = "Backpack Weight",
       y = "Number of Backpacks")
```


**Question 4.**  

What is the relationship between body weight and backpack weight?

```{r}
# There is a trend where as body weight increases backpack weight increases slightly 

ggplot(backpack) +
  aes(x = body_weight, y = backpack_weight) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Body Weight",
       y = "Backpacks Weight")
```


**Question 5.**  

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings. 

```{r}
# Women generally weigh less. Backpack weight increases more with body weight in females than males

ggplot(backpack) +
  aes(x = body_weight, y = backpack_weight, colour = sex) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Body Weight",
       y = "Backpacks Weight")
```


**Question 6.**  

What **proportion** of students report back pain?   
# 32/100 have back problems

```{r}
backpack_clean <- backpack %>% 
  mutate(back_problems = recode(back_problems,
                                "0" = "No",
                                "1" = "Yes"))

ggplot(backpack_clean, aes(x = "")) + 
  geom_col(aes(y = length(back_problems), fill = back_problems)) +
  coord_polar("y", start = 0) + 
    labs(title = "\nProportion of students who report back pain\n",
         y = "",
         x = "",
       fill = "Do they have back problems?") + 
    theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
```

**Question 7.**  

Is this proportion different between men and women? 
# There is a much higher percentage of back problems in women than men

```{r}
ggplot(backpack_clean, aes(x = "")) + 
  geom_col(aes(y = length(back_problems)/100, fill = back_problems, sex)) +
  labs(x = "Sex",
       y = "Count",
       title = "Proportion of back problems between men and women",
       fill = "Do they have back problems?")
```

**Question 8.**  

Now you've investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both `backpack_weight` and `body_weight` as well as the `ratio`.   

*Hint: faceting would be useful here*.   

```{r}
# This graph suggests if you have a high backpack weight to body weight ratio then you're far more likely to have back problems if you are women. 
ggplot(backpack_clean) +
  geom_col(aes(x = back_problems, y = ratio, fill = back_problems)) +
  facet_grid(~sex) +
  labs(x = "Back Problems",
       y = "Backpack Weight to Body Weight Ratio",
       title = "\nThe Impact of the Backpack Weight to Body Weight Ratio",
       subtitle = "(against Back Problems between the sexes)",
       fill = "Do they have back problems?") 
```

# Extensions

<br>

**Question 1.** 

Does reported backpain differ across the year groups? Ignore year 0 in your data.  


**Question 2.** 

Is there a difference between how heavy the bags those in different years carry?


