---
title: "Homework - CIs"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

<hr>

# MVP

Now we'll go back to CI creation in the normal fashion. We'll take the `ames` data from the CIs lab earlier today and regard it now as a **sample**, we won't be drawing any smaller samples from within it. This is the usual situation in an analysis: you use all the data available to you!

<br>

**Task 1.**  
Load the data again, `clean_names()`, and re-familiarise yourself with it

```{r}
library(tidyverse)
library(infer)
library(janitor)

ames <- read.csv("data/ames.csv") %>%
  clean_names()
                 
```

<br>

**Task 2.**  
Investigate the distribution of `lot_area`. Is the distribution roughly normal? If not, what problems do you find?

```{r}
# Long tail, right skew

ames %>% 
  ggplot() + 
  geom_histogram(aes(lot_area))
```

<br>

**Task 3.**  
Compute and visualise a bootstrap sampling distribution for the `mean(lot_area)` of the sold houses.

```{r}
bootstrap_ames <- ames %>%
    specify(response = lot_area) %>%
    generate(reps = 1000, type = "bootstrap") %>%
    calculate(stat = "mean") 

bootstrap_ames %>% 
  ggplot() + 
  geom_histogram(aes(stat))
```


<br>

**Task 4.**  
Use your bootstrap distribution to calculate a $95\%$ CI for `mean(lot_area)`, and visualise it on the distribution

```{r}
bootstrap_ames_95 <- bootstrap_ames %>% 
  get_ci(level = 0.95, type = "percentile") 

bootstrap_ames %>% 
  visualise(bins = 30) + 
  shade_ci(endpoints = bootstrap_ames_95)
```


<br>

**Task 5.**  
You would like to know the `mean(lot_area)` of the sold houses with higher confidence. Calculate the $99\%$ CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the $95\%$ CI? Does that make sense?

```{r}
# Broader, makes sense
bootstrap_ames_99 <- bootstrap_ames %>% 
  get_ci(level = 0.99, type = "percentile") 

bootstrap_ames %>% 
  visualise(bins = 30) + 
  shade_ci(endpoints = bootstrap_ames_99)
```


<br>

**Task 6.**  
Calculate the point estimate of the `mean(lot_area)`

```{r}
mean_ames <- bootstrap_ames %>% 
  summarise(mean = mean(stat))
```

<hr>

# Extension

<br>

**Task 1.**  
Calculate a point estimate and $95\%$ CI for the proportion of houses in the data built before 1920.  Does the number of `reps` you use matter? [Investigate `reps` from $200$ up to $50000$, memory of your laptop permitting].
<br><br>


```{r}
# The more reps, the more like a normal distribution it looks but overall doesn't make any difference

ames_pre_1920 <- ames %>% 
  filter(year_built < 1920)

bootstrap_ames <- ames_pre_1920 %>%
    specify(response = lot_area) %>%
    generate(reps = 1000, type = "bootstrap") %>%
    calculate(stat = "mean") 

bootstrap_ames_95 <- bootstrap_ames %>% 
  get_ci(level = 0.95, type = "percentile") 

bootstrap_ames %>% 
  visualise(bins = 30) + 
  shade_ci(endpoints = bootstrap_ames_95)

mean_ames <- bootstrap_ames %>% 
  summarise(mean = mean(stat))
```