---
title: "Clustering homework"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


* You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings. 

* We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers. 

* Perform k-means clustering and chose a value of k.

* Visualise the clustering for your chosen value of k.

* Do you think the clustering seems a good fit for this data?

* Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the 'Segmentation & clustering intro' lesson). 

```{r}
library(tidyverse)
library(janitor)
library(GGally)
```

```{r}
mall_customers <- read_csv("data/mall_customers.csv") %>% 
  clean_names() %>% 
  select(-customer_id)
```

```{r}
# No NAs
any(is.na(mall_customers))
```

```{r}
mall_customers %>% 
  ggpairs()
```

```{r}
mall_customers_trim <- mall_customers %>% 
  select(annual_income_k, spending_score_1_100)
```

```{r}
# Looks like there are 5 clusters but shall we see...
ggplot(mall_customers_trim) +
  aes(x = annual_income_k, y = spending_score_1_100) +
  geom_point() 
```

```{r}
mall_customers_scale <- mall_customers_trim %>% 
  mutate_if(is_numeric, scale)
```

```{r}
cluster_mall <- kmeans(mall_customers_scale, 
                      centers = 8, 
                      nstart = 25)
```

```{r}
library(broom)

tidy(cluster_mall,
     col.names = colnames(mall_customers_scale))

augment(cluster_mall, mall_customers)
```

```{r}
glance(cluster_mall)
```

```{r}
max_k <- 20 

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(mall_customers_scale, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, mall_customers)
  )

k_clusters %>% 
  unnest(glanced)
```

```{r}
clusterings <- k_clusters %>% 
  unnest(glanced) 

clusterings 
```

```{r}
# Looks like the elbow is at 5
ggplot(clusterings) +
  aes(x = k, y = tot.withinss) +
  geom_point() +
  geom_line() + 
  scale_x_continuous(breaks = seq(1,20, by = 1))
```

```{r}
# 5 clusters appears to be right
library(factoextra)
fviz_nbclust(mall_customers_scale, 
             kmeans,
             method = "silhouette", 
             nstart = 25)
```

```{r}
# Appears to say 1 cluster here but I think we can conclude from above that we'll go with 5
fviz_nbclust(mall_customers_scale, 
             kmeans,
             method = "gap_stat", 
             nstart = 25)
```

```{r}
# 5 appears to fit well
clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k == 5) %>% 
  ggplot() + 
   aes(x = annual_income_k, y = spending_score_1_100, colour = .cluster) +
  geom_point(aes(color = .cluster)) 
  #geom_text(aes(label = .cluster)) 
```

You could label: 
1 - High rollers
2 - Middle Class 
3 - Frugal folks
4 - Sensible low-income sues 
5 - Credit card bandits 

```{r}
# 5 appears to fit well
k5 <- clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k == 5)

# get cluster info for centres
k5clust <- k5 %>% 
  select(kclust) %>% 
  pull()
```


```{r}
# notice how the centres are fit to the scaled data
k5clust[[1]]$centers
```


```{r}
# define function to remove scaling
remove_center_scaling <- function(centre_mat, scaled_df) {
  vars <- colnames(centre_mat)
  
  unscaled_centres <- sapply(
    vars,
    function(x) centre_mat[, x] * attr(scaled_df[[x]], 'scaled:scale') +
      attr(scaled_df[[x]], 'scaled:center'))
  
  return(as_tibble(unscaled_centres))
}
```

```{r}
# call function. remove scaling from centroids
unscaled_centres <- remove_center_scaling(
  k5clust[[1]]$centers, mall_customers_scale
  )
```

```{r}
ggplot(k5) + 
  geom_point(aes(x = annual_income_k, y = spending_score_1_100,
                 colour = .cluster)) +
    geom_text(data = unscaled_centres,
              aes(x = .data[["annual_income_k"]],
                  y = .data[["spending_score_1_100"]]),
              color = "black", size = 4, label = 1:5) +
  stat_ellipse(data = k5,
               aes(x = annual_income_k, y = spending_score_1_100,
                   colour = .cluster, fill = .cluster),
               geom = "polygon", alpha = 0.1) + 
  labs(x = "Annual Income",
       y = "Spending Score")
```